Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-25 paper/paper.tex
Updates from Overleaf
Wrote training paragraph and table

\section{Related Work}
Text~\todo[noline]{Do this}
\subsection{Metadata for Image Collection}
Metadata development is intertwined with the development of digital technology. A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories. Examples of Descriptive schemes include X, y, z... Examples of technical schemes include... The use varies across communities, and application technique is primarily manual. Research evaluating such schemes XXX, show XXX.

@@

@@

\begin{verbatim}
|  category  | #instances   |  category  | #instances   |  category  | #instances   |
|:----------:|:-------------|:----------:|:-------------|:----------:|:-------------|
|    fish    | 297          |   ruler    | 1496         |    eye     | 456          |
|    two     | 100          |   three    | 100          |            |              |
|   total    | 2449         |            |              |            |              |

@@

Final: {"data_time": 0.006645713496254757, "eta_seconds": 0.0, "fast_rcnn/cls_accuracy": 0.984375,
"fast_rcnn/false_negative": 0.0, "fast_rcnn/fg_cls_accuracy": 1.0, "iteration": 99999,
"loss_box_reg": 0.054501257836818695, "loss_cls": 0.03908616118133068, "loss_mask": 0.06379510834813118,
"loss_rpn_cls": 0.0010549294238444418, "loss_rpn_loc": 0.005114196799695492, "lr": 0.02,
"mask_rcnn/accuracy": 0.9722937165937804, "mask_rcnn/false_negative": 0.012800597698663846,
"mask_rcnn/false_positive": 0.05609636495338312, "roi_head/num_bg_samples": 115.75,
"roi_head/num_fg_samples": 12.25, "rpn/num_neg_anchors": 246.5, "rpn/num_pos_anchors": 9.5,
"time": 0.3563086399990425, "total_loss": 0.15775199318886735}
\end{verbatim}\todo{Training details, will turn this into a paragraph on how model is created}
\subsection{Pixel Analysis}
The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect. They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box. To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.

@@

\end{verbatim}
\section{Discussion}
Text \textit{texty text}%~\cite{Lamport:LaTeX}
\section{Conclusion}
Text \textbf{text}

>>>>

\section{Related Work}
Text~\todo[noline]{Do this}
\subsection{Metadata for Image Collection}
\todo{Wasn't looking for a citation but stumbled upon this paper: \url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0207636}, might be worth a skim}
Metadata development is intertwined with the development of digital technology. A wide range of metadata standards are applicable to metadata supporting image description as well as technical aspects, and have been used in a range of image repositories. Examples of Descriptive schemes include X, y, z... Examples of technical schemes include... The use varies across communities, and application technique is primarily manual. Research evaluating such schemes XXX, show XXX.

@@

\section{Goal and Objectives}

@@

Our training dataset consisted of the following number of instances for each class:

\begin{table}[H]
    \centering
    \caption{Training dataset}
    \label{tab:dataset}
    \begin{tabular}{cc}
        \toprule
        \textbf{Class} & \textbf{Number of Instances}\\
        \midrule
        Fish & 297\\
        Ruler & 1496\\
        Eye & 456\\
        Two & 100\\
        Three & 100\\
      \bottomrule
\end{tabular}
\end{table}

All of the training data was labeled by hand using \verb|makesense.ai|.~\cite{make-sense} While the ultimate goal of the project is to generalize to images from a variety of specimen collections, we have thus far focused only on images from the INHS\ Fish Collection.~\cite{INHS} Using \verb|detectron|'s default training scheme, the model was trained for \(100,000\) epochs. All instance types were included in a single object detection model. The total loss\todo{Find and specify which loss function was used} began at \(2.948\) and ended at \(0.158\) for the training data.

\begin{comment}
\begin{verbatim}
|  category  | #instances   |  category  | #instances   |  category  | #instances   |
|:----------:|:-------------|:----------:|:-------------|:----------:|:-------------|
|    fish    | 297          |   ruler    | 1496         |    eye     | 456          |
|    two     | 100          |   three    | 100          |            |              |
|   total    | 2449         |            |              |            |              |

@@

Final: {"data_time": 0.006645713496254757, "eta_seconds": 0.0, "fast_rcnn/cls_accuracy": 0.984375,
"fast_rcnn/false_negative": 0.0, "fast_rcnn/fg_cls_accuracy": 1.0, "iteration": 99999,
"loss_box_reg": 0.054501257836818695, "loss_cls": 0.03908616118133068, "loss_mask": 0.06379510834813118,
"loss_rpn_cls": 0.0010549294238444418, "loss_rpn_loc": 0.005114196799695492, "lr": 0.02,
"mask_rcnn/accuracy": 0.9722937165937804, "mask_rcnn/false_negative": 0.012800597698663846,
"mask_rcnn/false_positive": 0.05609636495338312, "roi_head/num_bg_samples": 115.75,
"roi_head/num_fg_samples": 12.25, "rpn/num_neg_anchors": 246.5, "rpn/num_pos_anchors": 9.5,
"time": 0.3563086399990425, "total_loss": 0.15775199318886735}
\end{verbatim}
\end{comment}
\subsection{Pixel Analysis}
The masks and bounding boxes produced by \verb|detectron| are generally quite good, although they are almost never perfect. They almost always either include additional background as part of the fish, or clip part(s) of the fish outside the bounding box. To solve this shortcoming, we utilize pixel analysis methods commonly found in image informatics.

@@

\end{verbatim}

\todo{Randomly verify a sampling of length values}

\section{Discussion}
Text \textit{texty text}%~\cite{Lamport:LaTeX}
\subsection{Future Work}
\section{Conclusion}
Text \textbf{text}
